A preliminary constraint grammar for Russian

### 2015-03-25 2015-nodalida-ruscg/ruscg.tex
stuff}
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@59523 72bbbca6-d526-0410-a7d9-f06f51895060

\cite{yablonsky1999russian}

% det/prn (e.g. pos... их, я, мой)
% 'over'generation (e.g. all dets get all gen/nbr/case combinations)

>>>>

The morphological transducer used in this study is described in Author (2015). 
It is primarily based on Zaliznjak's ``Grammatical dictionary of Russian'', 
including the 2001 version's appendix of proper nouns. It also includes approximately CITE Grishina and Lyashevskaya 2008. http://dict.ruslang.ru/gram.php .

Example~\ref{ex:FSToutput} gives some examples of the output.

\ex. \label{ex:FSToutput} 
	\a. \rus{новый}+A+Msc+Inan+Sg+Nom
	\b. \rus{автомат}+N+Msc+Inan+Sg+Nom
	\c. 
% det/prn (e.g. pos... их, я, мой)
% 'over'generation (e.g. all dets get all gen/nbr/case combinations)
